### 2017-02-03 Manuscript/SW_early_life_telomeres.Rmd
Edits

4. Telomere length and the slope of the relationship with age varied markedly among cohorts. Telomere length was positively associated with island-wide temporal insect abundance - a key resource for the insectivorous Seychelles warbler - suggesting that the costs associated with living in harsher environments can be studied by investigating telomere dynamics. We also found evidence for sex-specific relationships between telomeres and tarsus length, potentially reflecting differential costs of growth, which leads to adult females having significantly shorter telomeres than males.

>>>>

4. Telomere length and the slope of the relationship with age varied markedly among cohorts. Telomere length was positively associated with island-wide temporal insect abundance - a key resource for the insectivorous Seychelles warbler - suggesting that the costs associated with living in harsher environments can be studied by investigating telomere dynamics. We also found evidence for sex-specific relationships between telomeres and tarsus length, potentially reflecting differential costs of growth.

### 2017-02-03 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Edits

dd3$Gainer <- ifelse(dd3$DeltaRTL>0,1,0)

Fig2C <- ddply(dd3,
           .(Agemonths),
           summarise,
           PropGainers = mean(Gainer),
           n = length(Gainer)) %>%
  subset(n > 20) %>%
  ggplot(aes(x = Agemonths,
           y = PropGainers)) +
  ylab("Proportion gainers") + 
  xlab("Age") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_point(col = 'grey')+
  geom_line(col = 'grey')+
  annotate('text',x = 0,y = 0.6,label = 'A')

@@

>>>>

temp <- subset(dd3,TimeDiff < 4)
temp$MidAge <- (temp$Agemonths+temp$Agemonths1)/2
temp$Gainer <- ifelse(temp$DeltaRTL>0,1,0)

Fig2C <- ggplot(temp, aes(x = Agemonths,
           y = Gainer)) +
  ylab("Proportion gainers") + 
  xlab("Age") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  geom_point(col = 'grey')+
  geom_count(alpha = 0.2)+
  geom_smooth()+
  annotate('text',x = -0.2,y = 1,label = 'C')

@@

ggplot(temp,aes(x = TimeDiff,y = DeltaRTL))+
geom_point()+
geom_smooth()
